Greenhouse gas emissions model - making scenarios

### 2021-11-11 GHG_model_report.Rmd
Add devtools options to load the latest version of decisionSupport

```{r, warning = F, include = F}
#install and load packages
library(DiagrammeR)
library(decisionSupport)
library(ggplot2)
library(kableExtra)
library(magrittr)
library(plyr)
library(rmarkdown)
#devtools::install_github("CWWhitney/uncertainty")
library(uncertainty)

>>>>

```{r, warning = F, include = F}
#install and load packages
library(DiagrammeR)
# devtools::install_github("eikeluedeling/decisionSupport")
library(decisionSupport)
library(ggplot2)
library(kableExtra)
library(magrittr)
library(plyr)
library(rmarkdown)
#devtools::install_github("CWWhitney/uncertainty")
library(uncertainty)

### 2021-11-11 Scenarios_report.Rmd
Add devtools options to load the latest version of decisionSupport

```{r, warning=FALSE, include=FALSE}
#install and load packages
library(DiagrammeR)
library(decisionSupport)
library(ggplot2)
library(kableExtra)
library(magrittr)
library(plyr)
library(rmarkdown)
# devtools::install_github("CWWhitney/uncertainty")
library(uncertainty)

>>>>

```{r, warning=FALSE, include=FALSE}
#install and load packages
library(DiagrammeR)
# devtools::install_github("eikeluedeling/decisionSupport")
library(decisionSupport)
library(ggplot2)
library(kableExtra)
library(magrittr)
library(plyr)
library(rmarkdown)
# devtools::install_github("CWWhitney/uncertainty")
library(uncertainty)
